Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-01 phd/dissertation/chapter5.tex
work on k+1 implies 1

\section{$k+1$-tactics and marks for $\gruKPGame{X}$}

@@

\begin{lem}
  Let $F\in \omega_1^{<\omega}$ and $m<\omega$.
  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$ as defined below.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    A = \{z^\frown \<1\> : z \in \{0\}^{<\omega}\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

@@

\begin{proof}
  TODO
  % Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
  % $r$ a subsequence of $s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  % Define $n:\mb X\to\omega$ by
  %   \[
  %     n(x)
  %       =
  %     \left\{
  %       \begin{array}{lcl}
  %         |s|+1
  %       & : &
  %         x = \<x',s\> \in X\times 2^{<\omega}
  %       \\
  %         0
  %       & : &
  %         x \in C
  %       \end{array}
  %     \right.
  %   \]
  % and use $n$ to define the $k+1$-tactic $\tau$ by
  %   \[
  %     \tau(\emptyset)=\sigma(\emptyset,0)
  %   \]
  %   \[
  %     \tau(t\concat\<x\>)
  %       =
  %     L_{n(x)}
  %       \cup
  %     \{x\}
  %       \cup
  %     \sigma(t\concat\<x\>,n(x))
  %   \]

  % Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
  % If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
  % $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
  % $\{\{p(n)\}:n<\omega\}$ locally finite.

  % Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
  % removing points in $C$. If $q(0)=p(0)$, then
  %   \[
  %     q(0)
  %       =
  %     p(0)
  %       \not\in
  %     \tau(\emptyset)
  %       =
  %     \sigma(\emptyset,0)
  %   \]
  % and for any other $q(n)=p(m+1)=$
\end{proof}

>>>>

\section{Tactics and marks for $\gruKPGame{X}$}

@@

\begin{defn}
  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    z_n:n\to\{0\}
  \]
  \[
    A = \{z_n^\frown \<1\> : n<\omega\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
\end{defn}

\begin{lem}
  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

@@

\begin{proof}
  Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  Define $r:\mb X\to\omega$ by
    \[
      r(x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          x = \<x',s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\<x\>)
        =
      L_{r(x)+1}
        \cup
      \{x\}
        \cup
      \sigma(\<x\>,r(x))
    \]

  Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
  If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
  $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
  $\{\{p(n)\}:n<\omega\}$ locally finite.

  Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
  removing points in $C$ with $p(f(i))=q(i)$ (note $f(i)\geq i$).
  It follows that
    \[
      q(0)
        =
      p(f(0))
        \not\in
      \tau(\emptyset)
        \cup
      \bigcup_{m<f(0)}\tau(\<p(m)\>)
        \supseteq
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]

  Denoting $q(n)=\<x_n',s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      q(n+1)
        =
      p(f(n+1))
        \not\in
      \tau(\emptyset)
        \cup
      \bigcup_{m<f(n+1)}\tau(\<p(m)\>)
    \]
    \[
        \supseteq
      \tau(\emptyset)
        \cup
      \bigcup_{m\leq n}\tau(\<p(f(m))\>)
        =
      \tau(\emptyset)
        \cup
      \bigcup_{m\leq n}\tau(\<q(m)\>)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m\leq n}\sigma(\<q(m)\>,|s_m|)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m\leq n}\sigma(\<q(m)\>,m)
    \]
  and $q(n+1)\not\in\tau(\<q(n)\>)\supseteq L_{|s_n|+1}$ gives
  $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $q$ is a legal attack on the winning Markov strategy $\sigma$, so
  the collection $\{\{q(n)\}:n<\omega\}$ is locally finite.
  and it follows that $\{\{p(n)\}:n<\omega\}$ is also locally finite.
\end{proof}

\begin{lem}
  If $\pl K\kmarkwin{k+1}\gruKPGame{\mathbb{X}}$, then
  $\pl K\markwin\gruKPGame{\mathbb{X}}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that for
  $s\in[\mb X]^{\leq k+1}$ and $n<\omega$, there exist
  $F(s,n)\in[\omega_1]^{<\omega}$ and $m(s,n)<\omega$ with
  \[
    \sigma(s,n)
      \subseteq
    K_{F(s,n)}'
      \cup
    L_{m(s,n)}
  \]
  Also, it may be assumed that $i<n$ and $\ran r \subseteq \ran s$ implies
  $F(r,i)\subseteq F(s,n)$ and $m(r,i)\leq m(s,n)$, as well as $n\leq m(s,n)$.
\end{proof}
